DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-04-04 paper/related.tex
Initial commit

\section{Related Work}
% discusstion
% - model is still quite small. cam we use bigger CNNs?
%% \fixme{What we want to say:
%%   1) We showed DNN is feasible on today's embedded computing
%%   platforms.
%%   2) But, the CNN model is rather smaller-kind with respect to today's
%%   state-of-the-art CNNs, which are much bigger.
%%   3) disscuss google's object detection api
%%   paper~\cite{huang2017speed}. 
%%   4) Applying these much more complex DNNs (such as google's detection
%%   models) may be challenging for embedded computing
%%   platforms.
%%   5) Two general approaches: (1) make it faster (computing workload
%%   remains the same) (2) reduce the workload itself (model compression
%%   or reduced precision etc.)}

@@

While continuing performance improvmenets in embedded computing
platforms will certainly make processing of these complex CNNs faster,
another actively investigated approrach is to reduce the required
computational complexity itself.
When a DNN is deployed in those implementations with limited
resources, such as memory and power, the floating-point operations
involved in the large matrix multiplications are a burdensome task.
Many recent advances in network compression showed promising results
in reducing such computational cost during the feedforward
process. The fundamental assumption in those techniques is that the
DNNs are redundant in their structure and representation. For example,
network pruning can thin out the network and provides a more condensed
topology~\cite{han2015deep}.
Another common compression method is to reduce the
quantization level of the network parameters, so that arithmetic
defined with the floating-point operations are replaced with low-bit
fixed-point counterparts. To this end, single bit quantization of the
network parameters or ternary quantization have been recently proposed
~\cite{hwang2014fixed,soudry2014expectation,kim2016bitwise,rastegari2016xnor,hubara2016binarized,beauchamp2006embedded,govindu2004analysis}.
In those networks, the inner product between the
originally real-valued parameter vectors is defined with XNOR followed
by bit counting, so that the network can greatly minimize the
computational cost in the hardware implementations. This drastic
quantization can produce some additional performance loss, but those
new binarized or ternarized systems provide a simple quantization
noise injection mechanism during training so that the additional error
is minimized to an acceptable level.

>>>>

\section{Related Work}\label{sec:related}
% discusstion
% - model is still quite small. cam we use bigger CNNs?
%% \fixme{What we want to say:
%%   1) We showed DNN is feasible on today's embedded computing
%%   platforms.
%%   2) But, the CNN model is rather smaller-kind with respect to today's
%%   state-of-the-art CNNs, which are much bigger.
%%   3) disscuss google's object detection api
%%   paper~\cite{huang2017speed}. 
%%   4) Applying these much more complex DNNs (such as google's detection
%%   models) may be challenging for embedded computing
%%   platforms.
%%   5) Two general approaches: (1) make it faster (computing workload
%%   remains the same) (2) reduce the workload itself (model compression
%%   or reduced precision etc.)}

@@

While continuing performance improvements in embedded computing
platforms will certainly make processing these complex CNNs faster,
another actively investigated approrach is to reduce the required
computational complexity itself.
When a DNN is deployed in those implementations with limited
resources, such as memory and power, the floating-point operations
involved in the large matrix multiplications are a burdensome task.
Many recent advances in network compression have shown promising results
in reducing such computational cost during the feedforward
process. The fundamental assumption in those techniques is that the
DNNs are redundant in their structure and representation. For example,
network pruning can thin out the network and provides a more condensed
topology~\cite{han2015deep}.
Another common compression method is to reduce the
quantization level of the network parameters, so that arithmetic
defined with the floating-point operations are replaced with low-bit
fixed-point counterparts. To this end, single bit quantization of the
network parameters or ternary quantization have been recently proposed
~\cite{hwang2014fixed,soudry2014expectation,kim2016bitwise,rastegari2016xnor,hubara2016binarized,beauchamp2006embedded,govindu2004analysis}.
In those networks, the inner product between the
originally real-valued parameter vectors is defined with XNOR followed
by bit counting, so that the network can greatly minimize the
computational cost in the hardware implementations. This drastic
quantization can produce some additional performance loss, but those
new binarized or ternarized systems provide a simple quantization
noise injection mechanism during training so that the additional error
is minimized to an acceptable level.
